---
title: "App_Store_Analysis"
author: Angelo Kwak
date: 12/16/2019
output: html_notebook
---

Purpose:
The purpose of this project is to analyze a number of trends in the Apple App Store. I chose to do this project using this data because I'm interested in mobile app development and currently have an application on the App Store. Specifically, my application is for music and social media, so I will be heavily analyzing these genres specifically. 

```{r}
# clean up workspace environment
rm(list = ls())
#Packages
library(mosaic)
library(tidyverse)
library(DataComputing)
library(party)
```

The chunk below loads all data from the two datasets regarding the Apple App Store
```{r}
#This dataset contains a number of analytics about over 7000 applications on the App Store.
#Information includes rating, price, genre, etc.

dataset_1 <- 'C:/Users/angel/Dropbox/Penn State/STAT 184/Project/App_Store_Analysis/AppleStore.csv'

App_Store_Data <- read.csv(file = dataset_1, header=TRUE, sep=",")

#This dataset contains a number of analytics about over 7000 applications on the App Store.
#Information includes rating, price, genre, etc.
dataset_2 <- 'C:/Users/angel/Dropbox/Penn State/STAT 184/Project/App_Store_Analysis/appleStore_description.csv'

App_Store_Description_Data <- read.csv(file = dataset_2, header=TRUE, sep=",")
```

## Sample of the App Store Dataset
```{r}
App_Store_Data %>%
  sample_n(size = 10)
```
## Sample of the Description Dataset
```{r}
App_Store_Description_Data %>%
  sample_n(size = 10)
```
# General Analysis
The first thing that I wanted to do with this dataset is gather some general statistics about the apps within the App Store.
```{r}
#This code displays the mean size of each app, app rating, and number of languages supported within an app.
App_Store_Data %>%
  summarise(num_apps = n(),
            mean_app_size = mean(size_bytes),
            mean_app_rating = mean(user_rating),
            mean_supported_languages = mean(lang.num))
```

## App Store Breakdown
The following is a general breakdown of the categories of apps in the App Store. Below is a chart containing the specific number of apps in each category, in addition to a plot showing these numbers. This plot shows a more visually appealing way of looking at just how diverse the App Store really is. Based on this data, it's very clear that games take up a very large population in the App Store. 
```{r}
App_Categories <- App_Store_Data %>%
  group_by(prime_genre) %>%
  summarise(num_on_store = n())

App_Categories
```

```{r}
ggplot(data=App_Categories,aes(x=prime_genre,y=num_on_store ,fill=prime_genre))+geom_bar(stat='identity',position='stack', width=.9)+theme(axis.text.x=element_text(angle = 90, vjust = 0.5))+ xlab('App Category') + ylab('Number on Store')
```


```{r}

#layer1 <- geom_point(data = App_Store_Data, aes(shape = user_rating))
#layer2 <- geom_point(data = App_Store_Data, aes(shape = user_rating_ver))

#App_Store_Data %>%
 # ggplot(aes(x = id, y = user_rating))+geom_point()

```

# Specific classification for Music and Social Media
```{r}
#music data
Music_App_Data <-
  App_Store_Data %>%
  filter(prime_genre == 'Music')

#social network data
Social_Network_App_Data <-
  App_Store_Data %>%
  filter(prime_genre == 'Social Networking')

#join the music data with it's description 
Music_With_Desc <- Music_App_Data %>%
left_join(App_Store_Description_Data, 'id' = 'id')

#join social network data withn its description
Social_With_Desc <- Social_Network_App_Data %>%
left_join(App_Store_Description_Data, 'id' = 'id')
```

```{r}
#get most rated and highest rated music app names
Highest_Rated_Music <-
  Music_With_Desc %>%
  filter(user_rating >= 3.5) %>%
  arrange(desc(rating_count_tot)) %>%
  select(track_name, size_bytes, user_rating, rating_count_tot, price, app_desc)

#get highest rated social media app names
Highest_Rated_Social <-
  Social_With_Desc %>%
  filter(user_rating >= 3.5) %>%
  arrange(desc(rating_count_tot)) %>%
  select(track_name, size_bytes, user_rating, rating_count_tot, price, app_desc)
```

The following graphs show a how the number of user ratings ranges based on the price. From this, I was able to view how the number of reviews can impact the overall rating of paid apps.
```{r}
#compare ratings and number of ratings for paid apps. 
Paid_Music <-
  Highest_Rated_Music %>%
  filter(price > 0.00)

paid_frame <- ggplot(data=Paid_Music,aes(x=price,y=rating_count_tot))+geom_point()+aes(colour=user_rating)+scale_y_log10() 

rating_count_standard <- geom_hline(yintercept = 1000)

paid_frame+rating_count_standard
```


```{r}
Paid_Social <-
  Highest_Rated_Social %>%
  filter(price > 0.00)

paid_frame <- ggplot(data=Paid_Social,aes(x=price,y=rating_count_tot))+geom_point()+aes(colour=user_rating)+scale_y_log10() 

rating_count_standard <- geom_hline(yintercept = 1000)

paid_frame+rating_count_standard
```


